---
title: "Report"
author: "KN"
date: "24/09/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Note the args include, eval, echo, message, warning
```{r load libraries, message=FALSE,warning=FALSE}
library(tidyverse)
library(knitr)
```

### **_Experimenting with eval:_**

```{r experimenting with eval1, eval=FALSE}
a <- 2
print(a)
```


```{r experimenting with eval2, eval=TRUE}
a <- 2
print(a)
```

### **_Experimenting with include:_**
* toggles providing code and output defined in code
```{r experimenting with inc1, include=FALSE}
a <- 5
print('hello')
```  
a is `r a` for False
```{r experimenting with inc2, include=TRUE}
a <- 5
print('hello')
```  
a is `r a` for True

### **_Experimenting with echo:_**
* always provides output defined in code, toggles wether to show code 
```{r experimenting with echo1, echo=T}
a <- 5
print('Hello')
```
is True
```{r experimenting with echo2, echo=F}
a <- 5
print('Hello')
```
is False




### Gun Murders:
```{r load data,echo=FALSE}
load('rda/murders.rda')
summary(murders)
```
#### Plot1: R generated image will scale automatically depending on display
```{r plot way 1, echo=FALSE}
murders %>% mutate(abb=reorder(abb,rate)) %>% 
  ggplot(aes(x=abb,y=rate))+
  geom_col()+
  coord_flip()+
  theme(axis.text.y = element_text(size =7))
```

#### Plot2: User provided image for display
```{r plot way 2,echo=FALSE}
img_path <- 'figs/barplot.png'
include_graphics(img_path)
```
